---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
library(ggplot2)
library(dplyr)
library(babynames)

library(babynames)
 babynames_riley_casey_1960_later <- babynames %>%
   filter(name %in% c("Riley", "Casey"), year >= 1960)
   babynames_riley_casey_1960_later

```

## Including Plots


### This is the babynames plot from Problem set 4
```{r}
   
ggplot(data = babynames_riley_casey_1960_later , mapping = aes(x = year, y = prop, color = sex )) +
  geom_line() +
  labs(title = "Comparison of Casey and Riley", x = "Proportion", y = "Year") +
  facet_wrap(~name) +
  scale_color_manual(values = c("orange", "forestgreen"))   
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
